SST_patterns

### 2020-04-16 SST_patterns.Rmd
update

ggplot(data =final_intensity, aes(x = intensity_mean)) +
  geom_histogram(aes(fill = product),  
                       position = "dodge", alpha=0.6) +
  # labs(x = "Duration (Days)", y = "Number of upwelling signals", colour = "Temperature products") +
  facet_wrap(~site) +
theme_bw() ---
title: "SST_patterns"
author: "Amieroh Abrahams"
date: "19 August 2019"
output: html_document

knitr::opts_chunk$set(
  comment = "R>",
  warning = FALSE,
  message = FALSE 
)
#update.packages() 
library(tidyverse)
library(lubridate)
library(ggpubr)
library(zoo)
library(FNN)
library(scales)
library(gridExtra)
library(circular)
library(fossil)
library(mapproj)
library(broom)
# library(ncdf4) # This was used to process NetCDF files in an earlier version
library(stringr)
library(doMC); doMC::registerDoMC(cores = 4)
library(fasttime)
library(xtable)
library(ncdf4) # library for processing netCDFs
library(data.table)
# library(plyr) # RWS: Never load the plyr package as it interferes with the tidyverse
library(heatwaveR)
library(grid)
library(ggthemes)
```

@@

metrics <- metric_4years %>% 
  mutate(year = year(date_start)) %>% 
  group_by(product, site) %>% 
  summarise(y = n(),
            mean_intensity = mean(intensity_mean),
            mean_dur = mean(duration),
            mean_cumIn = mean(intensity_cumulative)) %>% 
  rename(count = y)

# lmod <- lm(mean_intensity ~ mean_dur, data = metrics)
# summary(lmod)
# 
# glht(lmod, linfct = K)

>>>>

ggplot(data =final_intensity, aes(x = intensity_mean)) +
  geom_histogram(aes(fill = product),  
                       position = "dodge", alpha=0.6) +
  # labs(x = "Duration (Days)", y = "Number of upwelling signals", colour = "Temperature products") +
  facet_wrap(~site) +
```
# Loading in all the data created using the code bellow

@@

metrics <- metric_4years %>% 
  mutate(year = year(date_start)) %>% 
  group_by(product, site) %>% 
  summarise(y = n(),
            mean_intensity = mean(intensity_mean),
            mean_dur = mean(duration),
            mean_cumIn = mean(intensity_cumulative)) %>% 
  rename(count = y)
```
